---
title: "brnum_table"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Providing a simple way to load an Excel table with BrNums and adding a column with the corresponding P# IDs from the database
* optionally add the missing IDs to the table
* this could (should?) be packaged as an RScript taking an input file as parameter and some options to guide the data processing, saving a tab delimited (tsv) text file to be then loaded in Excel

```{r}
library(dplyr)
#-- connect to the database and load the subject info
library('RPostgreSQL')
dbp <- read.delim(".pgpass", sep=":", header=TRUE)
pg_db <- "rse"
pg_user <- subset(dbp, database=="rse")[[1,4]]
pg_pass <- subset(dbp, database=="rse")[[1,5]]
pg <- dbDriver("PostgreSQL")
con <- dbConnect(pg, dbname=pg_db, user=pg_user, password=pg_pass, host="gdebsrv")
qry <- "SELECT 'P'||trim(to_char(s.id, '00000')) as p_id, brnum, brint, 
    dx, sex, race, age, mod, pmi 
    FROM subjects s, dx d where d.id=s.dx_id ORDER BY 1";
subj <- dbGetQuery(con, qry)

message("Loaded data for ",nrow(subj), " subjects")
```
```{r}
qry <- "SELECT 'P'||trim(to_char(s.id, '00000')) as p_id, brnum, brint, dx, sex, race, age, mod, pmi 
 FROM subjects s, dx d where d.id=s.dx_id ORDER BY 1";
subj <- dbGetQuery(con, qry)
write.table(subj, file="subjects_phenodata.tab", row.names = F, sep = "\t", quote=F)
qry <- "SELECT s.name as rnum, 'P'||trim(to_char(p.id, '00000')) as p_id, 
 brnum, dx, sex, race, age
  FROM subjects p, dx d, samples s WHERE s.subj_id=p.id 
  AND d.id=p.dx_id ORDER BY 1"
samp <- dbGetQuery(con, qry)
write.table(samp, file="samples_phenodata.tab", row.names = F, sep = "\t", quote=F)

qry <- "SELECT t.name as dataset, s.name as rnum, x.sample_id, protocol, rin, 'P'||trim(to_char(p.id, '00000')) as p_id, 
 brnum, brint, dx, sex, race, age, pmi, bamfile
  FROM subjects p, dx d, samples s, exp_rnaseq x, datasets t WHERE s.subj_id=p.id 
  AND d.id=p.dx_id AND s.id=x.s_id AND t.id=x.dataset_id
  ORDER BY 1"
rnasmp <- dbGetQuery(con, qry)
write.table(rnasmp, file="rnaseq_samples_phenodata.tab", row.names = F, sep = "\t", quote=F)

```


Load the Excel file to add the subj_id column
```{r}
library(readxl)
#fn <- "FeinbergSampleID_LBR_10.07.2020.xlsx"
fn <- "BrNum_LIBDIntranet_031221.n2511.xlsx"
bxl <- as.data.frame(read_excel(fn))

#bxl$subj_id <- subj$p_id[ match(as.integer(gsub("Br","", bxl$`Br #`)), subj$brint) ]
bxl$brint=as.integer(gsub("Br","", bxl$BrNum))
bxl$subj_id <- subj$p_id[ match(bxl$brint, subj$brint)]

```

OPTIONAL: find the missing BrNums 
```{r}
xlm <- anti_join(subj, bxl, by="brint")
colnames(xlm)=c("subj_id", "BrNum", "brint", "PrimaryDx", "Sex", "Race", "AgeDeath", "Manner Of Death", "PMI")
bxladd <- rbind(bxl, xlm)
```

```{r}
## -- check if bxladd looks good, push it back in bxl
bxladd$brint <- NULL
bxl <- bxladd
```


Write the Excel data to a tab delimited file and a csv to be loaded in Excel:
```{r}

fw="BrNum_LIBDIntranet_031221.n2511.subj_id"
bxl$AgeDeath <- round(bxl$AgeDeath, digits = 1)
write.table(bxl, file=paste0(fw,".tab"), row.names = F, sep = "\t", quote=F)
write.csv(bxl, file=paste0(fw,".csv"), row.names = F )

```

